Exploring Design Space for Differentially Private Bayesian Inference

### 2018-12-29 ICML2019/main.tex
update experiments

\noindent In the following some of the plots show
mean error as a function of the datasize while one
is a whiskers-plot where the y-axis shows the average
accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
different balanced priors used. The boxes extend from the lower to the upper quartile values
of the data, with a line at the median. A notch on the box around the
median is also drawn to give a rough guide to the significance of
difference of medians; The whiskers extend from the box to show the
range of the data. A blue box in the plots represents our newly
designed exponential mechanism's behavior-- where the sensitivity is calibrated
w.r.t Hellinger distance-- while the yellow box next to
it represents the performance of a variation of the basic Laplace
mechanism presented in Section (\ref{sec_mechs}) with the same
settings: that is $\epsilon, \delta$, data, prior. The variation
considered performs a postprocessing on the released parameters so
that they are consistent. For instance when the sum of the noised
parameters is greater than $n$ we will truncate them so that they sum
up to $n$.

>>>>

\noindent In the following some of the plots show
mean error as a function of the datasize while one
is a whiskers-plot where the y-axis shows the average
accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
different balanced priors used. The boxes extend from the lower to the upper quartile values
of the data, with a line at the median. A notch on the box around the
median is also drawn to give a rough guide to the significance of
difference of medians; The whiskers extend from the box to show the
range of the data. A blue box in the plots represents the $\hexpmech$'s behavior-- where the sensitivity is calibrated
w.r.t Hellinger distance-- while the green box next to
it represents the performance of a variation of the basic Laplace
mechanism $\lapmech$, and red one is $\ilapmech$ presented in Section (\ref{sec_mechs}) with the same
settings: that is $\epsilon$, data, prior. The variation
considered performs a postprocessing on the released parameters so
that they are consistent. For instance when the sum of the noised
parameters is greater than $n$ we will truncate them so that they sum
up to $n$.
